BOAST

### 2018-03-20 Tutorial/presentation/Tutorial-BOAST-2.tex
Moved talk to presentation directory.

\lstdefinestyle{BOAST}{
  language=Ruby,
  basicstyle=\tiny\ttfamily,
  backgroundcolor=\color{white},
  frame=single,
  captionpos=b,
  morekeywords={BOAST, pr, decl, opn, close}
}

>>>>

\lstdefinestyle{BOAST}{
  language=Ruby,
  basicstyle=\tiny\ttfamily,
  keywordstyle=\color{javapurple}\bfseries,
  stringstyle=\color{javared},
  commentstyle=\color{javagreen},
  backgroundcolor=\color{white},
  morekeywords={BOAST, pr, decl, opn, close}
}
